\underline{\textit{Broader Impacts}}:
Due to my academic experience at a young age, I am committed to
ensuring that no child's love of astronomy will go unfostered in my
community. It is crucial that childen who love STEM, and specifically
astronomy, are reinforced that this is a valid future career and that
a graduate degree is possible for them. Growing up in rural Maine,
graduate degrees were few and far between, and even the percentage of
high school graduates attending a 2-4 year college was only around
50$\%$. In my current neighborhood, the Lyon Street Community within
Columbia, SC, \textbf{only $27\%$ of people graduated from high
school, $13\%$ have a bachelor's degree, $3\%$ have a master's degree,
and $0\%$ have a PhD.} I will use my STEM outreach experiences with
NASA's ARSET program, as well as the techniques I learned volunteering
in elementary school math classrooms in college and tutoring high
school students while at Goddard, to help foster excitement for STEM
in my community. By way of a plan that I outline in my research
statement, I hope to convince these students that \textbf{achieving
higher degrees is possible and valuable}, and break the viscious cycle
of supressed academic opportunities forming in my community.
\noindent\fontsize{10}{14}\selectfont

\

\noindent[1]J. D. R. Pierel, C. A. Nixon, E. Lellouch, L. N. Fletcher, G. L. Bjoraker, R. K. Achterberg, B. Bzard, B. E. Hesman, P. G. J. Irwin, and F. M. Flasar. D/H Ratios on Saturn and Jupiter from \textit{Cassini} CIRS. The Astronomical Journal, 154(5):178, 2017.
\noindent\fontsize{12}{14}\selectfont

%As an NSF Fellow over the course of the next three years, I will have
%two sources of broader impacts that affect the scientific and local
%communities respectively. First, 
